---
title: "Proposal"
author: "Yinqiao Yan"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MNIST

## Read data

Firstly, we use `readr::read_csv()` function to load the data preprocessed in Python. 
Note that the output of read_csv() is tibble.

```{r Read_data}
rm(list = ls(all = TRUE))

library(readr)
library(dplyr)
library(ggplot2)
library(factoextra)
library(plotly)
library(cluster)

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

mnist_vec_train <- read_csv("mnist_vec_train.csv", col_names = T, col_types = cols())
mnist_vec_test  <- read_csv("mnist_vec_test.csv",  col_names = T, col_types = cols())
```

Convert `tibbles` to `data.frame`

```{r preprocess}
df_train <- mnist_vec_train %>% t() %>% as.data.frame()
df_test  <- mnist_vec_test  %>% t() %>% as.data.frame()
```

We use the first 1000 rows to build a sub-dataset and implement the K-means method
to cluster these images (vectors). Notice that to implement K-means method `fviz_cluster`,
there cannot be one or more column(s) in the dataset which have constant value 
throughout for all the rows. Otherwise an error would be reported.

```{}
Error in prcomp.default(train, center = TRUE, scale = TRUE) :
cannot rescale a constant/zero column to unit variance
```

```{r subDat}
n_sub <- 300
df_train_sub <- df_train[1:n_sub,]

# Delete the all-zero columns.
idx0 <- (colMeans(df_train_sub) == 0)
df_train_sub_use <- df_train_sub[, !idx0]

cat("Number of columns that are all zero:", sum(idx0),"\n")
cat("New train df dim:", dim(df_train_sub_use))
```

We can see that there are 175 columns whose elements are all zeros.


```{r Kmeans}
fviz_nbclust(df_train_sub_use, kmeans, method = "wss",k.max=20) +
  geom_vline(xintercept = 8, linetype = 2)
km_res <- kmeans(df_train_sub_use, 8)
fviz_cluster(km_res, data = df_train_sub_use,
             ellipse = F,
             show.clust.cent = F,
             shape = 1,
             repel = F,
             pointsize = 0.5,
             labelsize = 6,
             geom = "text",
             ggtheme = theme_grey())
```

# CIFAR-10
